### 2018-05-22 latex/sc18/experiments.tex
minor fixes

\begin{figure}
\begin{tikzpicture}
\renewcommand{\datafile}{data/str_3D_HSI.dat}
\renewcommand{\numiterations}{10}
\liavastrue
\strongscalingplot
\end{tikzpicture}
\caption{Strong scaling of 3D HSI real world data with dimension 1024 x1344 x 33 on processor grids of $1 \times k \times k$ for $k \in {1, 2, 4, 8, 16, 32}$. The rank is fixed at 32.}
\label{fig:stronghsi3D}
\end{figure}

>>>>

\begin{figure}
\begin{tikzpicture}
\renewcommand{\datafile}{data/str_3D_HSI.dat}
\renewcommand{\numiterations}{10}
\liavastrue
\strongscalingplot
\end{tikzpicture}
\caption{Strong scaling of 3D HSI real world data with dimension 1024 x1344 x 33 on processor grids of $k \times k\times 1$ for $k \in {1, 2, 4, 8, 16, 32}$. The rank is fixed at 32.}
\label{fig:stronghsi3D}
\end{figure}
